Jean Pockets and Gender

### 2024-04-24 paper/paper.qmd
update

library(tidyverse)
library(tibble)
library(ggplot2)
library(dplyr)
library(janitor)
library(kableExtra)

@@

In this paper, the dataset used for analysis was obtained from `measurementRectangles.json`. This dataset mirrors the measurements found in `measurements.csv`, including brand, style, gender specification (men or women), product name, brand size, waist size, fabric composition, price, and height and width measurements of jean pockets  (see @tbl-raw_data). Notably, the dataset contains a "pocketArea" column representing the area of the polygon generated from a pocket's measurements. However, it's important to note that the units of measurement for this area are not explicitly specified in the provided metadata. To determine the units, one must examine how the measurements were collected and processed. Since the measurements were processed using computer-generated calculations and intended for web display, it is possible that the pocket area is denoted in square centimeters (px²). However, without explicit confirmation from the data documentation or creators of the dataset, absolute certainty regarding the units of measurement remains elusive.
\newpage

@@

head(women_jeans_data, 5) |>
  kable(
    format = "markdown",
    caption = "Women's Data",
    col.names = c("Price", "Pocket Area"),
    booktabs = TRUE
  )
```
\newpage

@@

In summary, the results suggest that pocket area is not a significant predictor of price for either men's or women's jeans in the dataset analyzed. Other factors not considered in this analysis are likely to have a greater influence on the pricing of jeans for both genders.
\newpage

>>>>

library(tidyverse)
library(tibble)
library(ggplot2)
library(dplyr)
library(janitor)
library(kableExtra)
library(knitr)

@@

For this paper, the dataset used for analysis was obtained from `measurementRectangles.json`. This dataset mirrors the measurements found in `measurements.csv`, including brand, style, gender specification (men or women), product name, brand size, waist size, fabric composition, price, and height and width measurements of jean pockets  (see @tbl-raw_data). Notably, the dataset contains a "pocketArea" column representing the area of the polygon generated from a pocket's measurements. However, it's important to note that the units of measurement for this area are not explicitly specified in the provided metadata. To determine the units, one must examine how the measurements were collected and processed. Since the measurements were processed using computer-generated calculations and intended for web display, it is possible that the pocket area is denoted in square centimeters (px²). However, without explicit confirmation from the data documentation or creators of the dataset, absolute certainty regarding the units of measurement remains elusive.
\newpage

@@

head(women_jeans_data, 5) |>
  kable(
    format = "markdown",
    caption = "Women's Data",
    col.names = c("Price", "Pocket Area"),
    booktabs = TRUE
  )

```
\newpage

@@

In summary, the results suggest that pocket area is not a significant predictor of price for either men's or women's jeans in the dataset analyzed. Other factors not considered in this analysis are likely to have a greater influence on the pricing of jeans for both genders.
